Investigating Fault-Proneness Through Hotfix Commits in the Light of Different Programming Languages

### 2016-02-22 msr_paper/main.tex
Some more fixes.

\begin{abstract}
Choosing the most suitable programming language is a challenging task for every project manager and developer. Often the success of a software project is determined by the stability of the system after a release. We analyse the prevalence of hotfix commits in various development areas as an indicator of which languages tend to produce the least amount of problems after software has been published. Based on the Boa September 2013 SourceForge dataset, we analysed the metadata from the 16 most popular project types and estimated the amount of deployed hotfixes to compare the fault-proneness of programming languages that are used across project types. Our results only identified 8 languages that are widely used across different domains: Java, C, C++, C\#, Perl, Python, PHP, and JavaScript. Java has the least number of hotfixes per version update (0.18), while C\# required most hotfixes per version update (0.34). We identified the Security and Internet \& Communications project types as being the most reliable (i.e.\ requiring least amount of hotfixes per version update). The analysis did not reveal conclusive patterns for language classes (strongly vs.\ weakly typed and dynamic vs.\ static).
\end{abstract}

@@

The main contributions of this paper are:
%
\begin{itemize}
  \item An  approach to identify hotfix commits in repositories.
  \item A quantitative analysis identifying fault-proneness of specific programming topics and the distribution of faults across programming languages. The analysis identified that only eight languages are used across the top 16 most popular domains identified by the Boa SourceForge 2013 dataset.
  \item An investigation on the impact of language classes on reliability: strongly-typed vs weakly-typed, static vs dynamic and scripting vs procedural. The investigation showed no clear patterns on the influence of language classes.
\end{itemize}
%
Related work is discussed in the next section. Section 3 explains our empirical study and its results, followed by conclusions and future work.

@@

\subsection{Comparison of programming languages}
%Throughout our investigation we discovered that there were a lot of authors that tried to utilize commit data to try to propose good engineering practices and find a way to determine code quality \cite{Agrawal2015}. Furthermore, there were several papers that compared and contrasted the performance of different languages, which led to our second research topic. We explored these existing scientific studies to see what techniques authors had implemented. We also analysed the hypotheses these papers proposed to increase the scope of our project.\par

@@

The main related work focussing on the effect of programming languages~\cite{Ray2014} is based on the rate of defect occurrences in various languages. The study was carried out on a huge dataset from GitHub (1.5 million commits). To evaluate the effect that programming languages have on software quality, the authors grouped languages according to their type, e.g.\ strongly vs.\ weakly typed. They also used mathematical methods to triangulate and produce statistics for how group size, project history and number of contributors affect the number of defects. In order to achieve more representative results, they took a sample of 17 languages and extracted the top 50 projects per language. The results showed how defect-prone languages are compared to others. This research focused on classifying bugs based on their type, while we focused specifically on the distribution of hotfixes across programming languages.

@@

Other work used different parameters to compare programming languages, for example, program length, programming effort, run-time efficiency, memory consumption, and reliability \cite{Prechelt2000}.  Fourment and Gilling~\cite{Fourment2008} analysed memory usage and speed of execution of three different bioinformatics methods for six distinct programming languages. This was especially pertinent as bioinformatics applications have huge datasets and computational time taken is not trivial, hence optimising speed is desirable.

@@

\subsection{Identifying bug fix commits}
%The first major problem we had to solve was identifying actual hotfix commits. Due to Boa's limitations, we were not able to find commit history from hotfix branch. We were only capable of collecting information with regard to commits performed on the main branch. Therefore, we reviewed various papers to identify the most appropriate method of determining the type of the commit to extract only the ones related to a bug correction.\par

@@

Our work was inspired by a previous research paper~\cite{Ray2014} which compared the number of bug fix commits to the total number of commits across 17 languages and 850 different projects. Our primary contribution is the investigation of the fault-proneness of different languages accross project domains based on the newly defined criteria \emph{hotfixes per version update}.

\subsection{Dataset}
We selected the Boa September 2013 SourceFourge dataset for this study as it containts project topics. From the dataset, we selected projects from the top 16 most popular project topics. This resulted in of 49,865 projects. Moreover, we only concentrate on projects that incorporate versioning (i.e.\ containing bump commits).

\subsection{Approach for identifying hotfix commits}
Our method to distinguish hotfixes based on commit messages has 2 parts:

@@

\subsection{Research questions}
\noindent Our study aimed to answer the following research questions:

\noindent\textbf{RQ1 (language popularity):} What languages are the most widely used across the top 16 most popular categories?

\noindent\textbf{RQ2 (hotfixes vs.\ project categories):} What project categories achieve the highest/lowest number of hotfixes per version update?

\noindent\textbf{RQ3 (hotfixes vs.\ languages):} What languages achieve the highest/lowest number of hotfixes per version update?

\noindent\textbf{RQ4 (hotfixes vs.\ language types):} Are there any relationships between the occurrences of hotfixes and the type of the programming language?

@@

		\hline
		Average & &  & & \textbf{0.25}&\textbf{0.17}&\textbf{0.28}&\textbf{0.28}&\textbf{0.28}&\textbf{0.47}&\textbf{0.33}&\textbf{0.17}&\textbf{0.12}&\textbf{0.32}&\textbf{0.27}&\textbf{0.34}&\textbf{0.53}&\textbf{0.11}&\textbf{0.27}&\textbf{0.32} \\
		\hline
	\end{tabular}
	\caption{Ratios of hotfix commits per version bump commits of 8 common languages and their 16 respective categories. $\mathcal{P}$, $\mathcal{C}$, and $\mathcal{T}$ represent the classes of the language. $\mathcal{P}$ stands for Programming Paradigm class (P=Procedural, S=Scripting). $\mathcal{C}$ is for Compilation class (S=Static, D=Dynamic), and $\mathcal{T}$ is for Type class (W=weakly-typed, S=Strongly-typed).}
	\label{tab:1}
\end{table*}

%\section{Results}
We performed an empirical study on the SourceForge dataset using our method of identifying version bump commits and hotfix commits. The findings are explained below.
\subsection{RQ1: language popularity}
Our investigation on the most widely used languages across the top 16 most popular categories revealed that there are surprisingly few such languages. We chose the languages based on their frequency of occurrence across 16 categories. From Table \ref{tab:1}, the 8 widely used languages include Java (16), C (15), C++ (15), Perl (11), Python (11), PHP (11), C\# (10), and JavaScript (7) respectively.  We found a significant drop in occurrence for the rest of languages so their results are not included here.  %One would expect JavaScript to appear in the list. However, it is present only in 7 categories and hence is ignored from the list. This may be due to the fact that JavaScript is mainly used only for website development while our 16 popular categories span over various aspects of software.

It is interesting that the majority of these languages are not used in Testing, which contains only Java, C, and C++. Similarity, only a few languages appear in Code Generators and Site Management categories.

@@

\subsection{RQ2: hotfixes vs.\ project categories}
To be able to compare among languages, we calculated their hotfix ratios. The hotfix ratio of a language $P$ in category $C$ is a ratio of total hotfix commits per total version bump commits of the language in that category. %We proceed to analyse why certain categories might have low numbers of hotfixes and vice versa.
\begin{equation*}
\mathrm{HotfixRatio}_{P,C} = \frac{\sum{\mathrm{HotfixCommit}_{P,C}}}{\sum{\mathrm{VersionBumpCommit}_{P,C}}}
\end{equation*}
In Table \ref{tab:1}, \textbf{Communications have the lowest average hotfix ratios across all categories (0.11)} followed by Internet, Security, and Systems Administration (0.12, 0.17, 0.17) respectively. These categories are information critical. They are expected to be tested extensively before deployment to reduce the chance of failure. This may result in fewer hotfixes being needed after deployment. An interesting observation is that the average hotfix ratio of C in Internet category is incredibly low (0.03). We believe that is because there are several new languages designed specifically for Internet applications. Not much new C code is being written in this area, which results in a very low number of hotfix commits. %Security categories  %This could be down to fully comprehensive testing techniques, but could also be attributed to the fact that within those categories, the language has been used for an extensive period and hence there is a lot of experience with a variety of different bugs, meaning they are less likely to occur during development as experienced programmers are less likely to make those particular mistakes in the first place. This could also be the reason the projects written in Perl have a very low hot fix average for all four categories.

On the other hand, the category with \textbf{the highest average hotfix ratio is Code Generators (0.53)}. C and C++, have very high average hot fix ratios while  PHP and Java are the lowest. One can speculate that PHP and Java are established languages for writing code generators and due to this engender low hot fix averages. C and C++ might share syntactic details and semantic structure that would result in a similar hot fix average between them.

The second least reliable category is Role playing (0.47) which has higher hotfix ratio than its superset, Game category. We believe that this specific kind of game is more complex with vast amount of configurations of characters and items in the game. It is common to release a few hotfixes after a new version release due to adjusting these configurations. %We can obviously see that all languages in Role Playing category have high average numbers of hot fixes per update.

@@

\subsection{RQ3: hotfixes vs.\ languages}
Language comparison based on the average hotfix ratio over all the categories in Table 1 has shown that \textbf{Java has the lowest average hotfix ratio (0.176)} followed by JavaScript (0.209) and Perl (0.218). However, all the mentioned languages show marginally better results with an approximately 8\%-difference compared to other common languages: PHP (0.282), C++ (0.286), C (0.305) and C\#(0.339). \textbf{C\# has the highest average hotfix ratio among all the languages.}

\subsection{RQ4: hotfixes vs.\ language types}
Another interesting research question is comparing the type of programming languages by their average hotfix ratios. The classification in Table \ref{tab:1} is inspired by \cite{Ray2014}, where languages were compared using hotfix ratios with respect to their three main classes. Programming Paradigm class (noted as $\mathcal{P}$ in Table \ref{tab:1}) has three variations: procedural, functional, and scripting. The Compilation class contains static and dynamic type. The final one, Type class, separates languages into strongly-typed and weakly-typed. According to \cite{Ray2014}, strongly-typed languages experienced fewer bug fixes than its counterpart, weakly-typed. Static programming languages required fewer corrective commits than dynamic ones. And finally, functional languages encountered fewer bug fixes than procedural ones.

Due to our criteria of selecting the languages, the chosen 8 languages are all either procedural or scripting, but not functional. Most probably this was due to the fact that functional languages are limited to specific use cases and as such are not widely popular across different domains  \cite{Wadler1999}. Consequently, we only compared procedural and scripting languages in this class.

\subsubsection*{Programming paradigm: procedural vs.\ scripting}
From Table \ref{tab:1}, there is no clear trend or pattern of the hotfix ratio among procedural (Java, C, C\#, C++) and scripting (Perl, Python, PHP) languages across all the categories. This is possibly because the number of data points (languages) were too low to observe such behaviours and draw any firm conclusions. %It was always the case that at least one of the languages would not follow a pattern. For some categories, the comparison would consider only one language from a certain category.

\subsubsection*{Compilation: static vs.\ dynamic}
In this class, static (Java, C, C\#, C++) and dynamic (Perl, Python, PHP) languages led to the same conclusions of no clear difference of observed hotfix ratios between the two sets as can be seen from Table \ref{tab:1}. The reason was because the languages in these two categories coincided with the languages in the first two classes (procedural and scripting).

\subsubsection*{Type: strongly-type vs.\ weakly-typed}
The third class compares strongly-typed (Java, C\#, Perl, Python) and weakly-typed (C, C++, PHP) languages. Similarly to the previous two classes, we encountered no clear pattern across the categories. Furthermore, we found problems of having comparisons against only one member of a language class. Solely in the Communications category, we were able to detect some pattern, where weakly-typed languages performed slightly better. However, there were only two languages labelled as weak. Therefore, we cannot reach any satisfying conclusions based on this finding.

@@

\section{Conclusions and Future Work}
We have presented a study on detecting the fault-proneness of programming languages through hotfix commits, a topic that has not been investigated so far. As part of our research we performed a topic-specific analysis across 16 programming domains (categories) to detect the most widely used languages. Languages and topics that achieved highest/lowest ratios of hotfix per version update were investigated and we tried to identify patterns based on the language classification presented in \cite{Ray2014}. We used Boa to mine repositories in the SourceForge September 2013's dataset. %Our goal was to verify whether the general relationships between languages' reliability holds with regard to hotfixes.  
We identified 8 languages as being the most popular across different domains including: Java, C, C++, Perl, Python, PHP, C\#, and JavaScript. We discovered that Java achieves the smallest hotfix/version update ratio (0.176), while C\# required the highest amount of hotfixes per version increase (0.339). From the different categories, we observed that Security, Internet and Communications are the most reliable (i.e. achieving the lowest hotfix/version update ratios), while Role Playing and Code Generation experienced the highest number of corrections by hotfixes. Finally, according to the language classes, we were not able to identify any conclusive patterns.

>>>>

\begin{abstract}
Choosing the most suitable programming language is a challenging task for every project manager and developer. Often the success of a software project is determined by the stability of the system after a release. We analyse the prevalence of hotfix commits in various development areas as an indicator of which languages tend to produce the least amount of problems after software has been published. Based on the Boa September 2013 SourceForge dataset, we analysed the metadata from the 16 most popular project topics and estimated the amount of deployed hotfixes to compare the fault-proneness of programming languages that are used across project domains. Our results only identified 8 languages that are widely used across different domains: Java, C, C++, C\#, Perl, Python, PHP, and JavaScript. Java has the least number of hotfixes per version update (0.18), while C\# required most hotfixes per version update (0.34). We identified the Security and Internet \& Communications project topic as being the most reliable (i.e.\ requiring least amount of hotfixes per version update). The analysis did not reveal conclusive patterns for language classes (strongly vs.\ weakly typed and dynamic vs.\ static).
\end{abstract}

@@

The main contributions of this paper are:
%
\begin{itemize}
  \item An  approach to identify hotfix commits in repositories.
  \item A quantitative analysis identifying fault-proneness of specific programming topics and the distribution of faults across programming languages. The analysis identified that only eight languages are used across the top 16 most popular domains (topics) identified by the Boa SourceForge 2013 dataset.
  \item An investigation on the impact of language classes on reliability: strongly-typed vs weakly-typed, static vs dynamic and scripting vs procedural. The investigation showed no clear patterns on the influence of language classes.
\end{itemize}
%
Related work is discussed in the next section. Section 3 explains our empirical study and its results, followed by conclusions and future work.

@@

\subsection{Comparison of Programming Languages}
%Throughout our investigation we discovered that there were a lot of authors that tried to utilize commit data to try to propose good engineering practices and find a way to determine code quality \cite{Agrawal2015}. Furthermore, there were several papers that compared and contrasted the performance of different languages, which led to our second research topic. We explored these existing scientific studies to see what techniques authors had implemented. We also analysed the hypotheses these papers proposed to increase the scope of our project.\par

@@

The main related work focussing on the effect of programming languages~\cite{Ray2014} is based on the rate of defect occurrences in various languages. The study was carried out on a huge dataset from GitHub (1.5 million commits). To evaluate the effect that programming languages have on software quality, the authors grouped languages according to their class, e.g.\ strongly vs.\ weakly typed. They also used mathematical methods to triangulate and produce statistics for how group size, project history and number of contributors affect the number of defects. In order to achieve more representative results, they took a sample of 17 languages and extracted the top 50 projects per language. The results showed how defect-prone languages are compared to others. This research focused on classifying bugs based on their type, while we focused specifically on the distribution of hotfixes across programming languages.

@@

Other work used different parameters to compare programming languages, for example, program length, programming effort, run-time efficiency, memory consumption, and reliability~\cite{Prechelt2000}.  Fourment and Gilling~\cite{Fourment2008} analysed memory usage and speed of execution of three different bioinformatics methods for six distinct programming languages. This was especially pertinent as bioinformatics applications have huge datasets and computational time taken is not trivial, hence optimising speed is desirable.

@@

\subsection{Identifying Bug Fix Commits}
%The first major problem we had to solve was identifying actual hotfix commits. Due to Boa's limitations, we were not able to find commit history from hotfix branch. We were only capable of collecting information with regard to commits performed on the main branch. Therefore, we reviewed various papers to identify the most appropriate method of determining the type of the commit to extract only the ones related to a bug correction.\par

@@

Our work was inspired by a previous research paper~\cite{Ray2014} which compared the number of bug fix commits to the total number of commits across 17 languages and 850 different projects. Our primary contribution is the investigation of the fault-proneness of different languages \emph{across} project domains (topics) based on the newly defined criteria \emph{hotfixes per version update}.

\subsection{Dataset}
We selected the Boa September 2013 SourceFourge dataset for this study as it contains project topics. From the dataset, we selected projects from the top 16 most popular project topics. This resulted in of 49,865 projects. Moreover, we only concentrate on projects that incorporate versioning (i.e.\ containing bump commits).

\subsection{Approach for Identifying Hotfix Commits}
Our method to distinguish hotfixes based on commit messages has two parts:

@@

\subsection{Research Questions}
\noindent Our study aimed to answer the following research questions:

\noindent\textbf{RQ1 (language popularity):} Which languages are the most widely used across the top 16 most popular topics?

\noindent\textbf{RQ2 (hotfixes vs.\ project topic):} Which project topics achieve the highest/lowest number of hotfixes per version update?

\noindent\textbf{RQ3 (hotfixes vs.\ languages):} Which languages achieve the highest/lowest number of hotfixes per version update?

\noindent\textbf{RQ4 (hotfixes vs.\ language class):} Are there any relationships between the occurrences of hotfixes and the class of the programming language?

@@

		\hline
		Average & &  & & \textbf{0.25}&\textbf{0.17}&\textbf{0.28}&\textbf{0.28}&\textbf{0.28}&\textbf{0.47}&\textbf{0.33}&\textbf{0.17}&\textbf{0.12}&\textbf{0.32}&\textbf{0.27}&\textbf{0.34}&\textbf{0.53}&\textbf{0.11}&\textbf{0.27}&\textbf{0.32} \\
		\hline
	\end{tabular}
	\caption{Ratios of hotfix commits per version bump commits of 8 common languages and their 16 respective topics. $\mathcal{P}$, $\mathcal{C}$, and $\mathcal{T}$ represent the classes of the language. $\mathcal{P}$ stands for Programming Paradigm class (P=Procedural, S=Scripting). $\mathcal{C}$ is for the Compilation class (S=Static, D=Dynamic), and $\mathcal{T}$ is for the Type class (W=weakly-typed, S=Strongly-typed).}
	\label{tab:1}
\end{table*}

%\section{Results}
We performed an empirical study on the SourceForge dataset using our method of identifying version bump commits and hotfix commits. The findings are explained below.
\subsection{RQ1: Language Popularity}
Our investigation on the most widely used languages across the top 16 most popular topics revealed that there are surprisingly few such languages. We chose the languages based on their frequency of occurrence across 16 topics. From Table \ref{tab:1}, the 8 widely used languages include Java (16), C (15), C++ (15), Perl (11), Python (11), PHP (11), C\# (10), and JavaScript (7) respectively.  We found a significant drop in occurrence for the rest of languages so their results are not included here.  %One would expect JavaScript to appear in the list. However, it is present only in 7 categories and hence is ignored from the list. This may be due to the fact that JavaScript is mainly used only for website development while our 16 popular categories span over various aspects of software.

It is interesting that the majority of these languages are not used in Testing, which contains only Java, C, and C++. Similarity, only a few languages appear in the Code Generators and the Site Management topics.

@@

\subsection{RQ2: Hotfixes vs.\ Project Topics}
To be able to compare among languages, we calculated their hotfix ratios. The hotfix ratio of a language $P$ in topic $C$ is a ratio of total hotfix commits per total version bump commits of the language in that topic. %We proceed to analyse why certain categories might have low numbers of hotfixes and vice versa.
\begin{equation*}
\mathrm{HotfixRatio}_{P,C} = \frac{\sum{\mathrm{HotfixCommit}_{P,C}}}{\sum{\mathrm{VersionBumpCommit}_{P,C}}}
\end{equation*}
In Table \ref{tab:1}, \textbf{Communications have the lowest average hotfix ratios across all topics (0.11)} followed by Internet, Security, and Systems Administration (0.12, 0.17, 0.17) respectively. These topics are information critical. They are expected to be tested extensively before deployment to reduce the chance of failure. This may result in fewer hotfixes being needed after deployment. An interesting observation is that the average hotfix ratio of C in the Internet topic is incredibly low (0.03). We believe that is because there are several new languages designed specifically for Internet applications. Not much new C code is being written in this area, which results in a very low number of hotfix commits. %Security categories  %This could be down to fully comprehensive testing techniques, but could also be attributed to the fact that within those categories, the language has been used for an extensive period and hence there is a lot of experience with a variety of different bugs, meaning they are less likely to occur during development as experienced programmers are less likely to make those particular mistakes in the first place. This could also be the reason the projects written in Perl have a very low hot fix average for all four categories.

On the other hand, the topic with \textbf{the highest average hotfix ratio is Code Generators (0.53)}. In this topic, C and C++ have very high average hot fix ratios while  PHP and Java have the lowest. One can speculate that PHP and Java are established languages for writing code generators and due to this engender low hot fix averages. C and C++ might share syntactic details and semantic structure that would result in a similar hot fix average between them.

The second least reliable topic is Role playing (0.47) which has higher hotfix ratio than its superset, the Game topic. We believe that this specific kind of game is more complex with vast amount of configurations of characters and items in the game. It is common to release a few hotfixes after a new version release due to adjusting these configurations. %We can obviously see that all languages in Role Playing category have high average numbers of hot fixes per update.

@@

\subsection{RQ3: Hotfixes vs.\ Languages}
The language comparison based on the average hotfix ratio over all the topics in Table 1 has shown that \textbf{Java has the lowest average hotfix ratio (0.176)} followed by JavaScript (0.209) and Perl (0.218). However, all the mentioned languages show marginally better results compared to other common languages: PHP (0.282), C++ (0.286), C (0.305) and C\#(0.339). \textbf{C\# has the highest average hotfix ratio among all the languages.}

\subsection{RQ4: Hotfixes vs.\ Language Classes}
Another interesting research question is comparing the class of programming languages by their average hotfix ratios. The classification in Table \ref{tab:1} is inspired by Ray et al.~\cite{Ray2014}, where languages were compared using hotfix ratios with respect to their three main classes. The Programming Paradigm class (noted as $\mathcal{P}$ in Table \ref{tab:1}) has three variations: procedural, functional, and scripting. The Compilation class contains static and dynamic typing. The final Type class separates languages into strongly-typed and weakly-typed. According to Ray et al.~\cite{Ray2014}, strongly-typed languages experienced fewer bug fixes than its counterpart, weakly-typed. Static programming languages required fewer corrective commits than dynamic ones. And finally, functional languages encountered fewer bug fixes than procedural ones.

Due to our criteria of selecting the languages, the chosen 8 languages are all either procedural or scripting, but not functional. Most probably this was due to the fact that functional languages are limited to specific use cases and as such are not widely popular across different domains~\cite{Wadler1999}. Consequently, we only compared procedural and scripting languages in this class.

\subsubsection*{Programming Paradigm: Procedural vs.\ Scripting}
From Table \ref{tab:1}, there is no clear trend or pattern of the hotfix ratio among procedural (Java, C, C\#, C++) and scripting (Perl, Python, PHP) languages across all the topics. This is possibly because the number of data points (languages) were too low to observe such behaviours and draw any firm conclusions. %It was always the case that at least one of the languages would not follow a pattern. For some categories, the comparison would consider only one language from a certain category.

\subsubsection*{Compilation: Static vs.\ Dynamic}
In this class, static (Java, C, C\#, C++) and dynamic (Perl, Python, PHP) languages led to the same conclusions of no clear difference of observed hotfix ratios between the two sets as can be seen from Table \ref{tab:1}. The reason was because the languages in these two classes coincided with the languages in the first two classes (procedural and scripting).

\subsubsection*{Type: Strongly-Typed vs.\ Weakly-Typed}
The third class compares strongly-typed (Java, C\#, Perl, Python) and weakly-typed (C, C++, PHP) languages. Similarly to the previous two classes, we encountered no clear pattern across the topics. Furthermore, we found problems of having comparisons against only one member of a language class. Solely in the Communications topic, we were able to detect some pattern, where weakly-typed languages performed slightly better. However, there were only two languages labelled as weak. Therefore, we cannot reach any satisfying conclusions based on this finding.

@@

\section{Conclusions and Future Work}
We have presented a study on detecting the fault-proneness of programming languages through hotfix commits, a topic that has not been investigated so far. As part of our research we performed a topic-specific analysis across 16 programming domains (topics) to detect the most widely used languages. Languages and topics that achieved highest/lowest ratios of hotfix per version update were investigated and we tried to identify patterns based on the language classification presented by Ray et al.~\cite{Ray2014}. We used Boa to mine repositories in the SourceForge September 2013 dataset. %Our goal was to verify whether the general relationships between languages' reliability holds with regard to hotfixes.  
We identified 8 languages as being the most popular across different domains including: Java, C, C++, Perl, Python, PHP, C\#, and JavaScript. We discovered that Java achieves the smallest hotfix/version update ratio (0.176), while C\# required the highest amount of hotfixes per version increase (0.339). From the different topics, we observed that Security, Internet and Communications are the most reliable (i.e. achieving the lowest hotfix/version update ratios), while Role Playing and Code Generation experienced the highest number of corrections by hotfixes. Finally, according to the language classes, we were not able to identify any conclusive patterns.
